Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-prune-regraft Graph

### 2015-03-23 curvature.tex
Illustration of SPR degree change lemma

We can improve these bounds in the case of adjacent trees.
To do so, we require the following lemma that characterizes exactly how the degree of a tree changes after an rSPR operation.

>>>>

We can improve these bounds in the case of adjacent trees.
To do so, we require the following lemma that characterizes exactly how the degree of a tree changes after an rSPR operation.
See Figure~\ref{fig:spr-degree-change} for an illustration of the Lemma.

\begin{figure}
	\hspace*{\stretch{1}}
	\includegraphics[width=\textwidth]{figs/spr-degree-change}
	\hspace*{\stretch{1}}
	\caption{An SPR move labelled as in Lemma~\ref{lem:degree_change}.
Moving the grey subtree $R$ from its position adjacent to $U$ in tree $T$ to its position adjacent to $V$ in tree $S$ changes the SPR degree by $2\left(k(a-b) + i - j\right)$.}
	\label{fig:spr-degree-change}
\end{figure}
